Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-09 dryad/README.Rmd
adding description of csv files

---
title: 'Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life"'
output:
  pdf_document:
      keep_md: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

@@

```{r, echo=FALSE}
file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv")
```

@@

@@

@@

```{r, echo=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")

```{r, echo=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")

```{r, echo=FALSE}
file.copy(from = ".../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.csv")

```{r, echo=FALSE}
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf")

  File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.pdf    
	File XXX Description: PDF file of r

@@

```{r}
files <- c()
text <- c()
for (file in 1:10) {

  text <- paste(text, 
                paste("DATA-SPECIFIC INFORMATION FOR:", file, "\\newline"))
}
text
```

>>>>

---
title: 'Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life"'
output:
  pdf_document:
    keep_md: yes
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  results = 'hide'
)
```

@@

```{r, echo = FALSE}

csv_file_names <- c("Sanchez-Reyes_etal_2022_table_1.csv",
                    "Sanchez-Reyes_etal_2022_table_2.csv",
                    "Sanchez-Reyes_etal_2022_supplementary_table_S1.csv",
                    "Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")
tre_file_names <- c("Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre")
```

```{r, echo=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv")
```

@@

```{r, echo=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv")
```

@@

```{r, echo=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")

```{r, echo=FALSE, eval=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf")

```{r, echo=FALSE, message=FALSE, }
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")

```{r, echo=FALSE, message=FALSE}
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf")

  File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.pdf    
	File XXX Description: PDF file version of file Sanchez-Reyes_etal_2022_supplementary_table_S2.csv.

@@

@@

```{r, echo = FALSE}
text <- c()
for (file_name in csv_file_names) {
  # read the csv file in:
  tt <- utils::read.csv(file = paste0("../dryad/", file_name), header = TRUE, row.names = NULL)
  # remove the column with row numbers:
  tt <- tt[,-1]
  # create the description text
  var_list <- paste("\\tab", gsub("[.]", " ", colnames(tt)))
  var_list <- paste(var_list, collapse = ": \\newline")
  text <- paste(text, 
                paste("DATA-SPECIFIC INFORMATION FOR:", file_name, "\\newline"),
                "1. Number of variables: ",
                ncol(tt), "\\newline",
                "2. Number of cases/rows:",
                nrow(tt), "\\newline",
                "3. Variable List: \\newline", var_list, "\\newline",
                "4. Missing data codes: None \\newline
                5. Abbreviations used: NA = not applicable \\newline \\newline")
}
```
